Efficient pedigree recording for fast population genetics simulation

### 2017-11-18 forwards_paper.tex
Remove old comment; s/delta/Delta in F

In so doing we record the \emph{population pedigree} --
the entire history of parent-offspring relationships of an entire population going back to a remote time --
as well as information encoding the genetic outcomes of each ancestral meiosis --
who inherited which parts of which parental chromosomes.
This embellished pedigree contains all the information necessary
to construct the genealogical tree that relates each individual to each other
at each position on the genome, i.e., the \emph{tree sequence}.
Combined with ancestral genotypes and the origins of new mutations,
it also completely specifies the genomic sequence of any individual in the population at any time.
This is much more than we need to know, however,
so we discard all information irrelevant to the genetic history
of the \emph{sampled} individuals,
which results in considerable savings.
Another way of representing this same information
is known as the \emph{ancestral recombination graph} ---
the {ARG} \citep{griffiths1997ancestral},
where nodes are common ancestor or recombination events ---
which has been the subject of substantial study
under the assumptions of coalescent theory \citep{wiuf1997number,wiuf1999ancestry,marjoram2006coalescent,wilton2015smc}.
\jda{would be nice to say, concisely the difference}

@@

\algstep{F2.}{Record trees till time $T - \delta$.}{ 
Simulate, using Algorithm~\algref{W} or another algorithm, $2N$ haploid
individuals using $\mathcal M$ to renumber the nodes, producing nodes $n$ and
edgesets $E$.
}

\algstep{F3.}{Simplification over $\delta$.}{
Select final samples $S'$ and using the simplification Algorithm~\algref{S},
simplify $n$ and $E$ to produce a simplified tree sequence.
}

>>>>

In so doing we record the \emph{population pedigree} --
the entire history of parent-offspring relationships of an entire population going back to a remote time --
as well as information encoding the genetic outcomes of each ancestral meiosis --
who inherited which parts of which parental chromosomes.
This embellished pedigree contains all the information necessary
to construct the genealogical tree that relates each individual to each other
at each position on the genome, i.e., the \emph{tree sequence}.
Combined with ancestral genotypes and the origins of new mutations,
it also completely specifies the genomic sequence of any individual in the population at any time.
This is much more than we need to know, however,
so we discard all information irrelevant to the genetic history
of the \emph{sampled} individuals,
which results in considerable savings.
Another way of representing this same information
is known as the \emph{ancestral recombination graph} ---
the {ARG} \citep{griffiths1997ancestral},
where nodes are common ancestor or recombination events ---
which has been the subject of substantial study
under the assumptions of coalescent theory \citep{wiuf1997number,wiuf1999ancestry,marjoram2006coalescent,wilton2015smc}.

@@

\algstep{F2.}{Record trees till time $T - \Delta$.}{ 
Simulate, using Algorithm~\algref{W} or another algorithm, $2N$ haploid
individuals using $\mathcal M$ to renumber the nodes, producing nodes $n$ and
edgesets $E$.
}

\algstep{F3.}{Simplification over $\Delta$.}{
Select final samples $S'$ and using the simplification Algorithm~\algref{S},
simplify $n$ and $E$ to produce a simplified tree sequence.
}
